Police Shootings and Racism in America

### 2020-10-18 police_eda.Rmd
fixed some stuff

all <- all %>% 
  select(-c("Date", "NatureOfStop", "Notes", "SubjectAge", "NumberOfShots", "Department", "FullNarrative", "fdate", "month", "day", "tr", "AvgAge", "VA", "F", "nshots", "sit")) %>% 
  mutate(b = as.numeric(b > 0),
         w = as.numeric(w > 0),
         l = as.numeric(l > 0),
         a = as.numeric(a > 0),
         so =  as.numeric(str_count(all$SubjectRace, "O") > 0),
         smale = as.numeric(str_count(all$SubjectGender, "M") > 0),
         sfem = as.numeric(str_count(all$SubjectGender, "F") > 0),
         ob = as.numeric(str_count(all$OfficerRace, "B") > 0),
         ow = as.numeric(str_count(all$OfficerRace, "W") > 0),
         ol = as.numeric(str_count(all$OfficerRace, "L") > 0),
         oa = as.numeric(str_count(all$OfficerRace, "A") > 0),
         oo =  as.numeric(str_count(all$OfficerRace, "O") > 0),
         omale = as.numeric(str_count(all$OfficerGender, "M") > 0),
         ofem = as.numeric(str_count(all$OfficerGender, "F") > 0),
         other = as.numeric(other), 
         replica = as.numeric(replica), 
         knife = as.numeric(knife), 
         gun = as.numeric(weapon == "gun"), 
         unarmed = as.numeric(weapon == "unarmed"),
         unknown_weapon = as.numeric(weapon == "U"),
         fatal = as.numeric(str_count(all$Fatal, "F") > 0)) %>% 
  select(-c(weapon, SubjectGender, OfficerRace, OfficerGender))

@@

```{r filter-all}
# Filter out unknown values
all <- all[-which(all$smale == 0 & all$sfem == 0),]
all <- all[-which(all$omale == 0 & all$ofem == 0),]
all <- all[-which(all$sb == 0 & all$sw == 0 & all$sl == 0 & all$sa == 0),]
all <- all[-which(is.na(all$sb)),]
all <- all[-which(all$ob == 0 & all$ow == 0 & all$ol == 0 & all$oa == 0),]
all <- all[-which(str_count(all$Fatal, "F") == 0 & str_count(all$Fatal, "N") == 0),]
all <- all %>% 
  select(-c(Fatal))
```

@@

>>>>

all <- all %>% 
  select(-c("Date", "NatureOfStop", "Notes", "SubjectAge", "NumberOfShots", "Department", "FullNarrative", "fdate", "month", "day", "tr", "AvgAge", "VA", "F", "nshots", "sit")) %>% 
  mutate(b = as.numeric(b > 0),
         w = as.numeric(w > 0),
         l = as.numeric(l > 0),
         a = as.numeric(a > 0),
         so =  as.numeric(str_count(all$SubjectRace, "O") > 0),
         smale = as.numeric(str_count(all$SubjectGender, "M") > 0),
         sfem = as.numeric(str_count(all$SubjectGender, "F") > 0),
         ob = as.numeric(str_count(all$OfficerRace, "B") > 0),
         ow = as.numeric(str_count(all$OfficerRace, "W") > 0),
         ol = as.numeric(str_count(all$OfficerRace, "L") > 0),
         oa = as.numeric(str_count(all$OfficerRace, "A") > 0),
         oo =  as.numeric(str_count(all$OfficerRace, "O") > 0),
         omale = as.numeric(str_count(all$OfficerGender, "M") > 0),
         ofem = as.numeric(str_count(all$OfficerGender, "F") > 0),
         weapon_other = as.numeric(other), 
         replica = as.numeric(replica), 
         knife = as.numeric(knife), 
         gun = as.numeric(weapon == "gun"), 
         unarmed = as.numeric(weapon == "unarmed"),
         unknown_weapon = as.numeric(weapon == "U"),
         fatal = as.numeric(str_count(all$Fatal, "F") > 0)) %>% 
  select(-c(weapon, SubjectGender, OfficerRace, OfficerGender))

@@

```{r filter-all}
# Filter out unknown values
all <- all[-which(all$smale == 0 & all$sfem == 0),]
all <- all[-which(all$omale == 0 & all$ofem == 0),]
all <- all[-which(all$sb == 0 & all$sw == 0 & all$sl == 0 & all$sa == 0 & all$so == 0),]
all <- all[-which(is.na(all$sb)),]
all <- all[-which(all$ob == 0 & all$ow == 0 & all$ol == 0 & all$oa == 0 & all$oo == 0),]
all <- all[-which(str_count(all$Fatal, "F") == 0 & str_count(all$Fatal, "N") == 0),]
all <- all %>% 
  select(-c(Fatal))
```

@@

```{r single_victims-race}
tempsb <- single_victims %>% 
  group_by(sb, fatal) %>% 
  summarise(count = n())

ggplot(tempsb, aes(x = sb, y = count, fill = fatal)) +
  geom_bar(stat="identity") + 
  labs(x = "Fatal", y = "Count", title = "Counts for Fatal vs. Non-Fatal Police Shootings")

tempsw <- single_victims %>% 
  group_by(sw, fatal) %>% 
  summarise(count = n())
tempsa <- single_victims %>% 
  group_by(sa, fatal) %>% 
  summarise(count = n())
tempsl <- single_victims %>% 
  group_by(sl, fatal) %>% 
  summarise(count = n())
tempso <- single_victims %>% 
  group_by(so, fatal) %>% 
  summarise(count = n())

### 2020-10-18 submissionii.Rmd
fixed some stuff

```{r num_rows, eval = F}
final_eda <- final_df %>%
  mutate(
      fatal = case_when(
        fatal == 1 ~ "Fatal",
        fatal == 0 ~ "Non-Fatal"
    )
  )

@@

```{r, eval = F}
tempsb <- single_victims %>% 
  group_by(sb, fatal) %>% 
  summarise(count = n())
tempsw <- single_victims %>% 
  group_by(sw, fatal) %>% 
  summarise(count = n())
tempsa <- single_victims %>% 
  group_by(sa, fatal) %>% 
  summarise(count = n())
tempsl <- single_victims %>% 
  group_by(sl, fatal) %>% 
  summarise(count = n())

## why are there no others?
tempso <- single_victims %>% 
  group_by(so, fatal) %>% 
  summarise(count = n())

@@

|       Upon first glance, there appears to be 1,883 incidents in the final dataset in which there was only one victim, and 148 with multiple victims. Among these,

>>>>

```{r num_rows, eval = F}
final_eda <- final_df %>%
  mutate(
      fatal = case_when(
        fatal == 1 ~ "Fatal",
        fatal == 0 ~ "Non-Fatal"),
      sb = case_when(
        sb == 1 ~ "Victim Type Present",
        sb == 0 ~ "Victim Type Not Present"
      ),
      sw = case_when(
        sw == 1 ~ "Victim Type Present",
        sw == 0 ~ "Victim Type Not Present"
      ),
      sl = case_when(
        sl == 1 ~ "Victim Type Present",
        sl == 0 ~ "Victim Type Not Present"
      ),
      sa = case_when(
        sa == 1 ~ "Victim Type Present",
        sa == 0 ~ "Victim Type Not Present"
      ),
      so = case_when(
        so == 1 ~ "Victim Type Present",
        so == 0 ~ "Victim Type Not Present"
      ),
      ob = case_when(
        ob == 1 ~ "Officer Type Present",
        ob == 0 ~ "Officer Type Not Present"
      ),
      ow = case_when(
        ow == 1 ~ "Officer Type Present",
        ow == 0 ~ "Officer Type Not Present"
      ),
      ol = case_when(
        ol == 1 ~ "Officer Type Present",
        ol == 0 ~ "Officer Type Not Present"
      ),
      oa = case_when(
        oa == 1 ~ "Officer Type Present",
        oa == 0 ~ "Officer Type Not Present"
      ),
      oo = case_when(
        oo == 1 ~ "Officer Type Present",
        oo == 0 ~ "Officer Type Not Present"
      )
  )

@@

```{r, eval = F}
tempsb <- single_victims %>% 
  group_by(sb, fatal) %>% 
  summarise(count = n())
tempsw <- single_victims %>% 
  group_by(sw, fatal) %>% 
  summarise(count = n())
tempsa <- single_victims %>% 
  group_by(sa, fatal) %>% 
  summarise(count = n())
tempsl <- single_victims %>% 
  group_by(sl, fatal) %>% 
  summarise(count = n())
tempso <- single_victims %>% 
  group_by(so, fatal) %>% 
  summarise(count = n())

@@

|       Upon first glance, there appears to be 1,906 incidents in the final dataset in which there was only one victim, and 148 with multiple victims. Among these,
